\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks, colorlinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\hypersetup{%
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    citecolor = black,    
    urlcolor=teal,
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pdfgentounicode=1

\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Niharika Sinha} \\ \vspace{1pt}
    \href{mailto:nihu2501@gmail.com}{\faicon{envelope} \underline{nihu2501@gmail.com}} $|$  
    \href{https://linkedin.com/in/nihx25}{\faicon{linkedin} \underline{LinkedIn}} $|$
    \href{https://github.com/nihx25}{\faicon{github} \underline{GitHub}} $|$
    \href{tel:+919650273974} {\faicon{phone} \underline{+919650273974}}
    
\end{center}

%--------------SUMMARY----------------
\section{Summary}
{Highly driven Front-end Developer with a passion for creating visually appealing and user-friendly web applications. Adept in utilizing HTML, CSS, Bootstrap, animation, jQuery, JavaScript, and React to design and develop responsive and interactive websites. Possessing strong problem-solving skills and the ability to work efficiently in a fast-paced environment. Committed to continuous self-improvement and delivering exceptional user experiences through creative and innovative coding solutions. Seeking an opportunity to challenge and advance technical abilities in a dynamic work environment.}

%-----------WORK EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubSubheading
    {\textbf{\href{https://verification.givemycertificate.com/v/94bfc238-5031-4eaa-8a45-5e6355310612}{Technical Coding Research (TCR) Innovation}} (Front-end Web Developer) }{Jan 2022 - March 2022}
    \resumeItemListStart
       \resumeItem{Completed a front-end developer internship at Technical Coding Research (TCR) Innovation, acquiring hands-on experience in HTML, CSS, Bootstrap, animation, jQuery, JavaScript, and React.}
       \resumeItem{Implemented React components to build modular and scalable web solutions. Used Bootstrap and animation to enhance the visual appeal and interactivity of websites.}
       \resumeItem{Improved problem-solving and critical thinking skills through hands-on projects and coding challenges.}
       \resumeItem{Received certification for successful completion of the internship program.}
    \resumeItemListEnd
   \resumeSubHeadingListEnd
%-------------------------------------------

%-----------Project Experience-----------
\section{Project Experience}
 \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/nihx25/nixform}{NixForm }}{[ HTML, CSS, React]}}{March 2023 - Present}
          \resumeItemListStart
            \resumeItem{Developed a web-based form using React, that allows users to collect and analyze data similar to Google Forms.}
            \resumeItem{Designed a user-friendly interface with responsive design principles, navigation, \& error handling.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    

    %  \resumeSubHeadingListStart
    %   \resumeProjectHeading
    %       {\textbf{\href{https://github.com/nihx25/car_animation}{2D Car Animation }}{[ HTML, CSS, JavaScript ]}}{January 2023}
    %       \resumeItemListStart
    %         \resumeItem{Created the visual design of the animation using HTML and CSS(The motion of car in x-y axis)}
    %         \resumeItem{Developed the animation's functionality using JavaScript(The motion of car controlled by the Enter button)}
    %         \resumeItem{Demonstrated proficiency in web design and development technologies such as HTML, CSS, and JavaScript through the creation of this project.}
    %       \resumeItemListEnd
    % \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/nihx25/Internet_speedChecker} {Internet Speed Checker }}{[ Python ]}}{January 2023}
          \resumeItemListStart
           \resumeItem{Utilized a specialized internet speed checking library to accurately measure and display the user's internet speed.}
           \resumeItem{Managed dependencies and virtual environments to ensure project stability and compatibility.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/nihx25/img_editor}{Img Editor }}{[ HTML, CSS, JavaScript ]}}{December 2022}
          \resumeItemListStart
            \resumeItem{Designed and coded a user-friendly interface to simplify the image editing process.}
            \resumeItem{Displayed creativity and innovation in using coding to develop a unique and functional image editor.}
            \resumeItem{Developed functionality for photo uploading, color conversion, rotation, and cropping.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://nihx25.github.io/Simon/} {Simon : Short-term memory skill game }}{[ HTML, CSS, JQuery ]}}{June 2021}
          \resumeItemListStart
           \resumeItem{Designed and developed a web-based version of the popular electronic game.}
           \resumeItem{Implemented game logic and UI features such as randomized patterns, score tracking, and audio feedback.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Awards and Certifications:-----------
\section{Awards and Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \resumeItemListStart
            \resumeItem{\textbf{\href{https://www.hackerrank.com/certificates/d46860607443}{HackerRank DSA Certification}}: Demonstrated proficiency in data structures and algorithms and have completed the basic and intermediate levels.}
            
      \resumeItemListEnd
    }}
 \end{itemize}

%
%-----------SKILLS-----------
\section{Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \resumeItemListStart
                \resumeItem{ C $|$ C++ $|$ Java $|$ Python $|$ JavaScript $|$ TypeScript  $|$ Shell $|$ SQL}
                \resumeItem{ React $|$ Node.js $|$ Flask $|$ Django $|$ Spring Boot $|$ OpenCV $|$ Git $|$ Scrum}
                \resumeItem{ Linux $|$ AWS $|$ Distributed Systems $|$ Frontend}
                \resumeItem{ English, Hindi - \textit{All professional proficiency or above}}
            \resumeItemListEnd
        }}
    \end{itemize}

 
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kalinga Institute of Industrial Technology (KIIT)}{Bhubaneswar, Odisha}
      {Bachelor of Technology in Computer science and engineering (BTech CSE)}{2020 -- Expected. 2024}
      \resumeItem{Pre-final (Third) year (CGPA 8.98)}

    \resumeSubheading
      {DAV Public School [ CBSE ]}{Faridabad, Haryana}
      {12th Grade (82\%)}{2019}

    \resumeSubheading
      {DAV Public School [ CBSE ]}{Faridabad, Haryana}
      {10th Grade (92\%)}{2017}
  \resumeSubHeadingListEnd
\end{document}
